A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-08-05 paper.tex
Fix grammar and typos

\begin{abstract} 
%cite IoT data subscription economy
Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy to share and trade their resources. Monetizing the real-time data on top of publish/subscribe (pub/sub) communication model enables the payment of data streams with data usage instead of a particular price for a fixed data set, which is similar to Software-as-a-Service (SaaS), a subscription-based pricing model. This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe. However, streaming data increases the importance and difficulties of dynamic data ownership and identity verification. A trustless data trading infrastructure is required where the entities can trade, validate data ownership and integrity without trusting any services. In addition, an automated subscription procedure is also demanded for the sake of data monetization. In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage built upon cryptographic message protocols allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
\end{abstract}

@@

\section{Introduction}
In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS}, and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing mechanism where data providers and data consumers meet.

%publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity and high variety of real-time "Big Data" streams\cite{BigData}. As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline. For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication. While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV. Therefore, the publish/subscribe (pub/sub) communication model that provides the flexibility of following and unfollowing the data streams for users is more appropriate in the IoT scenarios.

% SaaS
The economic incentive model in our proposed IoT data trading platform works as subscription service that valuates the payments by data usage. The subscription-based models (e.g. SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams. And for service consumers, they can subscribe and unsubscribe the services at will at anytime. The subscription-based model can easily adapt the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform. In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depend on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading. Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform. In current systems, trusted third-party authority like certificate authority (CA) is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}. Besides CA and storage, the subscription history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well. The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.

Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following five essential ones:
\begin{itemize}
	\item \textbf{Scalability}. 
1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible. 
	\item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.	
	\item \textbf{Confidentiality}. 
1) Only the authorized participants can access data streams. 2) Legitimate participants can always retrieve data even if they're dropped from the network.	
	\item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
	\item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to the quality control. 
\end{itemize}

Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design. In this paper, we investigate the use of decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure. See Fig.~\ref{fig:system_design}. The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, the digital rights of participants are protected. Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity, but also enables access control and provides a scalable key and data management.

\subsection{Contributions}
The contributions in the paper are summarized as follow:
\begin{itemize}
	\item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading, and to enable participants to automate the trading procedures and secure digital assets exchange across different organizations.
	\item We apply the subscription-based services economic model to adapt the features of IoT streaming data, and clarify the importance of using a decentralized identity system for trading.
	\item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensure the privacy of using the protocol.
	\item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with date product.
\end{itemize}

\subsection{Paper Organization}
The rest of this paper is organized as follows. In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures and distributed data storage are analyzed. In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture is illustrated. In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices. In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained. The analysis results are given in Section~\ref{section:evaluation}. Finally, we conclude the paper in Section~\ref{section:conclusion} and the future work in Section~\ref{section:future_work}.

@@

%TODO: cite IOTAIndustryMarketplace
\section{Related Work}
\label{section:relatedWork}
% pub/sub
\subsection{The Publish/subscribe Communication Models Over Blockchain}
The pub/sub service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in pub/sub system built on top of blockchain focused on the reliability, scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.

M. B. Abdullahi and G. Wang\cite{centralPubSub} presented a secure pub/sub data storage service in Wireless sensor networks (WSNs) which ensures several security issues. Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests. Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised. However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system, e.g., single point failure. G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. With the help of Ethereum smart contract, users can perform data validation easily, and brokers can keep track of data status. But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully.

In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties. The subscribers request publisher directly and ask them to save a cache space for interested data. The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environment to perform such functionalities and preserve data. Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data. Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain. The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent. The reputation system and the punishment rules against malicious acts of subscribers and publishers. Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides. Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.

@@

\subsection{Trusted IoT Trading Infrastructure}
Multiple infrastructures for trusted IoT data trading have been proposed by Paolo Missier et. al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts. The brokers are only responsible for data transmission in order to adapt flexible agreement between participants. Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other. However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.

@@

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange. This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet. A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold. Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading. However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper. Though taking IPFS as data storage instead of MAM is more efficient due to the current growth of underlying DLT, the chance of data losses and the effeciency of IPFS remain, which will be further discussed in Section.~\ref{section:distributed_storage}.

Researches below adopt MAM as data storage and a secure data transmission layer. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading. Service requesters call for proposal of interested data and accept/reject proposals from service providers. After a proposal is accepted, the requesters can access data streams stored via MAM and pay providers in IOTA tokens. This proposal matching and trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}. Nevertheless, this trading model does not take into account the refund and unsubscribe mechanism, the service requesters still need to pay even if they want to unsubscribe or the data does not meet expectations.

O. Lamtzidis and J. Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm. The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadata of data streams, and evaluates data price according to its quality. Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures. The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players. And the pricing strategy allows buyout, but does not take subscribe/unsubscribe based diagram into consideration. The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without the existence of any intermediate server but data providers only, data providers attach and trade data streams via MAM. With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.

\subsection{Distributed Storage System}
\label{section:distributed_storage}
Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems as data storage and also an incentive layer to encourage people get involved in the network.

Filecoin \cite{FileCoin} in Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, which users can obtain the data with the unique hash value through the network. Furthermore, considering the data may loss in the network, IPFS provides \textbf{pin} command for users to store the contents locally that will not be removed. However, the IoT sensor devices have limited space which is not appropriate to preserve generated data. Also, users can have a hard time finding the contents quickly if data is not widely available, the large amount of IPFS nodes and contents. Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retreiving process. Nevertheless, the efficiency problems still occur if the dedicated network grows larger.

Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then cipher text is sent to the Sia nodes that rent the storage in Siacoin through smart contracts. Files are duplicated in multiple nodes to prevent data loss.

\section{System Design Thinking}
\label{section:design_thinking}
\subsection{Data subscription-based trading platform players}
There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. As shown in Fig.~\ref{fig:pub_sub_model}.

@@

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored. One can easily prove himself by sharing the identifier on MAM without any authority.

Currently, considering the efficiency of uploading large files, IPFS performs better than MAM (i.e., writing contents to IOTA network). However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated to powerful proxy servers which is illustrated in Section.~\ref{section:ta_endpoint}. Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retreiving efficiency.

In our work, MAM build the trust of the platform while meeting the requirements of data trading which can be concluded below:

\begin{itemize}
    \item \textbf{Scalability}:
	\begin{itemize}
		\item Benefits from the underlying Tangle network, the system scales when more participants and more transactions join the network. 
    	\item For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
    \end{itemize}    
    \item \textbf{Integrity}: 
	\begin{itemize}    	
        \item Messages published to the Tangle are tamper-proof that against malicious modification.
    	\item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
    \end{itemize}
    \item \textbf{Confidentiality}:
    \begin{itemize}    	
    	\item The encrypted data are uploaded that only participants that have keys can decrypt.
    	\item The authorized users can retrieve data streams, since data is written on the Tangle which can be queried as long as the IOTA network is alive.
    	\item MAM provides forward-secrecy. The entry points of future data can be derived, but it's impossible to trace back those in the past. This feature prevents adversaries from retrieving published history even if the key is revealed.
    \end{itemize}
\end{itemize}

@@

The centralized identity model may have single point failure in identifier management and security issues like data leakage. With sensitive information holding on certain authorities, the leakage caused by cyber attacks or unscrupulous organizations trading user data damage the users' privacy. Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others. The decentralized identity model give back the controls of data to users that can resolve the aforementioned concerns in the centralized one.

In the decentralized identity model, every entity has a Decentralized Identifiers (DID\cite{DID} defined by W3C that contains identity information such as public key, unique identifiers of services and metadata. The digital footprints of entities is made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments. If a VC is verified via issuer's public key, the message will be labelled as trusted. Fig.~\ref{fig:did_vc} shows the relationship of VC issuer, verifier and user.

@@

In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of steps are addressed below:

>>>>

\begin{abstract}
%cite IoT data subscription economy
Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy to share and trade their resources. Monetizing the real-time data on top of the publish/subscribe (pub/sub) communication model enables the payment of data streams with data usage instead of a particular price for a fixed data set, which is similar to Software-as-a-Service (SaaS), a subscription-based pricing model. This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe. However, streaming data increases the importance and difficulties of dynamic data ownership and identity verification. A trustless data trading infrastructure is required where the entities can trade, validate data ownership and integrity without trusting any services. In addition, an automated subscription procedure is also demanded for the sake of data monetization. In this paper, we leverage the usages of distributed ledger technologies (DLTs) to construct a decentralized data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage built upon cryptographic message protocols allows transmitting, accessing, and validating data streams over distributed ledgers without authorities, and the digital rights of trading participants deserve a guarantee, which is enabled by design.
\end{abstract}

@@

\section{Introduction}
In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS}, and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding the number of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data trading platform is viewed as a solution to build a secure, reliable, and scalable data sharing mechanism where data providers and data consumers meet.

%publish/subscribe 的機制符合 IoT 應用情境，因為只在意部份資料
In contrast to the architectures in \cite{DIaas, MARSA} that target to handle static data sets, we aim for processing the high volume, high velocity, and high variety of real-time "Big Data" streams\cite{BigData}. As streaming data is composed of records at every moment, users or devices are interested in data of a specific time period instead of the whole timeline. For example, the Internet of Vehicles (IoV) allows vehicles to connect with traffic signs and bicycles, share information, and at the same time be able to understand the real-time environmental conditions and find the best route through the communication. While vehicles and traffic lights continuously generate information, a device only needs to process the data streams of surroundings but all appliances in the IoV. Therefore, the publish/subscribe (pub/sub) communication model that provides the flexibility of following and unfollowing the data streams for users is more appropriate in the IoT scenarios.

% SaaS
The economic incentive model in our proposed IoT data trading platform works as a subscription service that valuates the payments by data usage. The subscription-based models (e.g. SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming, and software, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams. And for service consumers, they can subscribe and unsubscribe the services at will at any time. The subscription-based model can easily adapt the underlying pub/sub communication model and benefit both data providers and consumers which promotes good circulation of the platform. In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership, and trading. Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform. In current systems, a trusted third-party authority like certificate authority (CA) is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of the entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate the General Data Protection Regulation (GDPR)\cite{GDPR}. Besides CA and storage, the subscription history of data consumers may reveal his/her interests and the exposure of personal information during trading process against GDPR as well. The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.

Among the challenges of data trading platform\cite{BigDataMarket} and the requirements mentioned above, we conclude the following five essential ones:
\begin{itemize}
    \item \textbf{Scalability}.
1) The performance of the platform should scale with the massive amount of participants. 2) The keys and entry points of data products managed by participants should be as small as possible.
    \item \textbf{Integrity}. 1) Prevent unauthorized modifications. 2) Ensure the accuracy and validity of contents.
    \item \textbf{Confidentiality}.
1) Only the authorized participants can access data streams. 2) Legitimate participants can always retrieve data even if they're dropped from the network.
    \item \textbf{Privacy}. Avoid revealing sensitive information of all participants, such as IP address and data consumers' habits which may leak within the subscription history.
    \item \textbf{Economics Incentive}. The economic incentives can encourage the data providers to participate in the system and pay more attention to quality control.
\end{itemize}

Taking all the requirements and the features of streaming data into consideration, the data trading platform for IoT towards a decentralized and trustless design. In this paper, we investigate the use of a decentralized publish/subscribe (pub/sub) model and DLTs to construct the authority-less and trusted infrastructure. See Fig.~\ref{fig:system_design}. The pub/sub model features the scalability and resource-efficiency, and DLTs resolve the trust of the service, since data and contracts (i.e., smart contracts) written on DLTs are transparent, immutable, and enforced automatically, the digital rights of participants are protected. Lastly, an end-to-end encrypted transmission protocol built on top of DLT is used as data storage, which not only ensures the data integrity but also enables access control and provides a scalable key and data management.

\subsection{Contributions}
The contributions in the paper are summarized as follow:
\begin{itemize}
    \item We investigate the usage of DLTs and distributed data storages in order to propose a decentralized architecture for IoT trading and to enable participants to automate the trading procedures and secure digital assets exchange across different organizations.
    \item We apply the subscription-based services economic model to adapt the features of IoT streaming data and clarify the importance of using a decentralized identity system for trading.
    \item We evaluate the performance and concerns of adopting an end-to-end encrypted transmission protocol, and propose an alternative approach for low-level devices to adopt this protocol while ensuring the privacy of using the protocol.
    \item We analyze the cost of designed smart contract to estimate the minimum data product price for data providers to sustain a product and the minimum cost for data consumers to interact with data products.
\end{itemize}

\subsection{Paper Organization}
The rest of this paper is organized as follows. In Section~\ref{section:relatedWork}, some related work of pub/sub over blockchain, decentralized data trading infrastructures, and distributed data storage are analyzed. In Section~\ref{section:design_thinking}, the components of proposed subscription-based data trading architecture is illustrated. In Section~\ref{section:MAM}, the end-to-end encrypted transmission protocol is introduced along with the protocol delegation solution for low-level devices. In Section~\ref{section:trading_model}, the trading models of proposed architecture are well explained. The analysis results are given in Section~\ref{section:evaluation}. Finally, we conclude the paper in Section~\ref{section:conclusion} and the future work in Section~\ref{section:future_work}.

@@

%TODO: cite IOTAIndustryMarketplace
\section{Related Work}
\label{section:relatedWork}
% pub/sub
\subsection{The Publish/subscribe Communication Models Over Blockchain}
The pub/sub service model consists of publishers, subscribers, and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in the pub/sub system built on top of blockchain focused on the reliability, scalability, and the different security issues such as, encrypted data communication, privacy-preserving data subscription, and access control of the digital asset.

M. B. Abdullahi and G. Wang\cite{centralPubSub} presented a secure pub/sub data storage service in Wireless sensor networks (WSNs) which ensures several security issues. Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests. Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised. However, the access control and encryption keys of data are enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system, e.g., single-point failure. G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers and applied DLTs to build a distributed pub/sub system that promotes the transparency of interactions of participants and the status of data. With the help of the Ethereum smart contract, users can perform data validation easily, and brokers can keep track of data status. But data is plaintext on blockchain, in which the privacy problem of sensitive data needs to be considered carefully.

In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties. The subscribers request publisher directly and ask them to save a cache space for interesting data. The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environments to perform such functionalities and preserve data. Also, the rights for accessing digital assets are more compatible in the IoT scenarios instead of copying raw data. Secure Pub-Sub model\cite{SPS}, a brokerless of pub/sub model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain. The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment, and data sharing are deployed on smart contracts that allow all operations are transparent. The reputation system and the punishment rules against malicious acts of subscribers and publishers. Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match both sides. Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in the ciphertext.

@@

\subsection{Trusted IoT Trading Infrastructure}
Multiple infrastructures for trusted IoT data trading have been proposed by Paolo Missier et. al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace that enables trading with Ethereum smart contracts. The brokers are only responsible for data transmission in order to adapt flexible agreement between participants. Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other. However, the data cubes (i.e., a tuple of information, such as provider, subscriber, and time period) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single-point failure still exists.

@@

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange. This research takes MAM as a data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet. A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered key and entry points management with MAM that minimizes the information which data producers need to hold. Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading. However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of the system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper. Though taking IPFS as data storage instead of MAM is more efficient due to the current growth of underlying DLT, the chance of data losses and the efficiency of IPFS remain, which will be further discussed in Section.~\ref{section:distributed_storage}.

The researches below adopt MAM as data storage and a secure data transmission layer. The industrial data marketplace\cite{IOTAIdustryMarketplace} proposed by IOTA Foundation targets for IoT data streams trading. Service requesters call for proposals of interested data and accept/reject proposals from service providers. After a proposal is accepted, the requesters can access data streams stored via MAM and pay providers in IOTA tokens. This proposal matching and the trading procedure can be automated without any human guidance\cite{IOTAIdustryMarketplaceWithoutHuman}. Nevertheless, this trading model does not take into account the refund and unsubscribe mechanism, the service requesters still need to pay even if they want to unsubscribe or the data does not meet expectations.

O. Lamtzidis and J. Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm. The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadata of data streams, and evaluates data price according to its quality. Furthermore, the Back-End server operates a user-friendly interface of the marketplace and tackles all trading procedures. The heavy loading of Back-End server encounters the system scalability problem, single-point failure as well as malicious attacks which may damage the profits of all players. And the pricing strategy allows buyout but does not take subscribe/unsubscribe based diagrams into consideration. The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without the existence of any intermediate server but data providers only, data providers attach, and trade data streams via MAM. With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.

\subsection{Distributed Storage System}
\label{section:distributed_storage}
Decentralized storage systems allow users to store files in a distributed network that is maintained by individual nodes around the world instead of a central service provider. Nevertheless, DLTs are often used as the backbone of these systems like data storage and also an incentive layer to encourage people to get involved in the network.

Filecoin \cite{FileCoin} in the Inter-Planetary File system (IPFS) is an incentive layer to incent nodes to provide storage. IPFS is a content-based addressing storage model in a peer-to-peer network, in which users can obtain the data with the unique hash value through the network. Furthermore, considering the data may lose in the network, IPFS provides \textbf{pin} command for users to store the contents locally that will not be removed. However, the IoT sensor devices have limited space which is not appropriate to preserve generated data. Also, users can have a hard time finding the contents quickly if data is not widely available, the large amount of IPFS nodes and contents. Thus, several pinning services like Pinata provide multiple IPFS nodes around the world to pin users' contents and charge by the size and replicas of contents, and users can even join the dedicated network to speed up the retrieving process. Nevertheless, the efficiency problems still occur if the dedicated network grows larger.

Sia\cite{Sia} splits the uploaded file into multiple data segments encrypted with the owner's private key, then ciphertext is sent to the Sia nodes that rent the storage in Siacoin through smart contracts. Files are duplicated in multiple nodes to prevent data loss.

\section{System Design Thinking}
\label{section:design_thinking}
\subsection{Data subscription-based trading platform players}
There are three major roles, data providers, data consumers, and brokers which are similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each other, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. As shown in Fig.~\ref{fig:pub_sub_model}.

@@

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data that can be verified by the hash of the whole pack of data, it consists of continually granular records of each time slot. Therefore, the verification such as, data integrity and source identity is narrow down to a data point as well. In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored. One can easily prove himself by sharing the identifier on MAM without any authority.

Currently, considering the efficiency of uploading large files, IPFS performs better than MAM (i.e., writing contents to IOTA network). However, IOTA network scales when more users and transactions join, and the MAM operations can be delegated to powerful proxy servers which is illustrated in Section.~\ref{section:ta_endpoint}. Furthermore, adopting IPFS in IoT scenarios may meet the challenges of data loss and data retrieving efficiency.

In our work, MAM builds the trust of the platform while meeting the requirements of data trading which can be concluded below:

\begin{itemize}
    \item \textbf{Scalability}:
    \begin{itemize}
        \item Benefits from the underlying Tangle network, the system scales when more participants and more transactions join the network.
        \item For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
    \end{itemize}    
    \item \textbf{Integrity}:
    \begin{itemize}
        \item Messages published to the Tangle are tamper-proof against malicious modification.
        \item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
    \end{itemize}
    \item \textbf{Confidentiality}:
    \begin{itemize}
        \item The encrypted data are uploaded that only participants that have keys can decrypt.
        \item The authorized users can retrieve data streams since data is written on the Tangle which can be queried as long as the IOTA network is alive.
        \item MAM provides forward-secrecy. The entry points of future data can be derived, but it's impossible to trace back those in the past. This feature prevents adversaries from retrieving published history even if the key is revealed.
    \end{itemize}
\end{itemize}

@@

The centralized identity model may have the single-point failure in identifier management and security issues like data leakage. With sensitive information holding on certain authorities, the leakage caused by cyber-attacks or unscrupulous organizations trading user data damage the users' privacy. Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others. The decentralized identity model give back the controls of data to users that can resolve the aforementioned concerns in the centralized one.

In the decentralized identity model, every entity has a Decentralized Identifiers (DID\cite{DID} defined by W3C that contains identity information such as public key, unique identifiers of services and metadata. The digital footprints of entities are made up of Verifiable Credential (VC) added to their DIDs, issued by trusted issuers, such as schools and government departments. If a VC is verified via the issuer's public key, the message will be labeled as trusted. Fig.~\ref{fig:did_vc} shows the relationship of VC issuer, verifier and user.

@@

In the Fig.~\ref{fig:MAM_E2EE}, we illustrate each step in the presented E2EE process. The details of the steps are addressed below:
